---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# C-vine regression

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version/cvinereg)](https://CRAN.R-project.org/package=cvinereg) [![R-CMD-check](https://github.com/jobstdavid/cvinereg/workflows/R-CMD-check/badge.svg)](https://github.com/jobstdavid/cvinereg/actions) [![version](https://img.shields.io/badge/version-0.1.0-green.svg?style=flat)](https://github.com/jobstdavid/cvinereg)

<!-- badges: end -->

An R package for C-vine copula based mean and quantile regression.

## Installation

You can install the development version from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("jobstdavid/cvinereg")
```

## Example

```{r example1, eval = T}
library(cvinereg)

# simulate data
set.seed(2024)
x <- matrix(rnorm(200), 100, 2)
y <- x %*% c(1, -2)
data <- data.frame(y = y, x = x)

# fit vine regression model
(fit <- cvinereg(y ~ ., data))

# summary of fit
summary(fit)

# show marginal effects for all selected variables
plot_effects(fit)
```

## Contact

Feel free to contact [jobstd\@uni-hildesheim.de](mailto:jobstd@uni-hildesheim.de) if you have any questions or suggestions.

## References

* Tepegjozova and Czado (2019), D- and C-vine quantile regression for large data sets, https://mediatum.ub.tum.de/doc/1536070/1536070.pdf.
* Tepegjozova et al. (2022). Nonparametric C- and D-vine-based quantile regression, Dependence Modeling, 10(1), 1-21, https://doi.org/10.1515/demo-2022-0100.
